Ecological performance of detecting data fabrication with summary statistics

### 2016-09-22 archive/response_ori_rev.md

# Response to reviewers ORIIR160019-01-00

We thank the reviewer for the time taken to look at and think about our proposal. Below, we respond point-by-point to the different weaknesses mentioned by the reviewer.

# Reviewer remark 1
The application does not provide clear evidence that the type of misconduct to which scientists admit is aligned with the kind of misconduct that the proposed methods would be able to address.

## Response

We never aimed to support such claim; we only aimed to sketch the problem with the way estimates of data fabrication are now constructed.

# Reviewer remark 2

The application did not explain why it only focuses on social and medical sciences.

## Response

We focus only on the social- and medical sciences given the widespread use of randomized experimental procedures and our familiarity with the measures applied here. We could expand to other fields with sufficient resources, but given the constraints of the current grant scheme we focused on these fields.

# Reviewer remark 3

The Principal Investigator does not have experience overseeing a large project given that he is still emerging as a scientist in a Ph.D. program.

## Response

The PI will be supervised during this process by the PhD supervisors, who cumulatively have managed projects amounting to approximately 4 million euro's.

# Reviewer remark 4

There is no investigator with qualitative analysis experience.

## Response

The research team is embedded in a methods and statistics department, with experts on qualitative analysis who will be queried, if necessary, during the project.

# Reviewer remark 5

Many literatures have suggested the possibility of using automatic tools to screen for data anomalies, so the
idea proposed is not innovative.

## Response

We did not intend to propose this to be our innovation --- we only wanted to implement the idea after repeated suggestions.

# Reviewer remark 6

There are some weaknesses in Project 1, which include: 1) The application does not consider the situation where researchers do not fabricate the entire data but only modify some numbers in real data, 2) Researchers can improve the way they fabricate data if they know what kinds of statistical methods are used for fabrication detection, 3) Twenty participants might not cover all or most of fabrication behaviors, and 4) There is a possibility that none of the methods can distinguish genuine data from fabricated data. Therefore, it is unclear how the applicant will continue to Project 2 and 3.

## Response

Project 1 is indeed limited by focusing on only fabrication and not falsification. We hope to expand on this in Phase II. With respect to the prob

Weakness 1: The reviewer correctly identifies that the projects only look at fabrication, and not falsification. This is a limitation and we look to improve upon this in the Phase II grant proposal.

Weakness 2: Detecting data fabrication will become a cat-and-mouse game indeed, as the reviewer points out. However, there is always the higher-dimensional aspect. If a researcher fabricates data that cannot be detected as such at the univariate level, detecting data fabrication can be done at all the higher levels still (bivariate, then trivariate, etc.). At some point the fabrication process will become so complicated in order to not be detected, that it is more effortful to fabricate data than to actually conduct a study.

Weakness 3: Twenty participants is most likely not as variable as we would want to have our results. Note that this number is the result of a feasibility analysis based on the contents of the project, the strain on the participants, and the resources available.

Weakness 4: Project 2 and 3 can continue regardless of the success of methods used in Project 1, given that if the methods fail Project 2 is more important (how did they fabricate and is it reasonable that the results did not pick this up + what new methods would have picked it up?). Project 3 is infrastructure development and will not actually apply the methods from project 1 because it does not extract the raw data, so it is independent of the results of project 1 (the infrastructure is used to extract information for analysis, the analysis method is not fixed). Moreover, we have inspected similar methods based on summary results that proved to be effective. Hence, we are confident that Project 1 will be successful.

# Reviewer remark 7

The application does not make a convincing case that the limited timeframe available to study participants to construct fabricated data is relevant to contexts where actual fabrication takes place.

## Response

Given the remark by the reviewer, we discussed this issue and adjusted our protocol to allow the time spent fabricating the data to be at the discretion of the participant. They will be invited to participate and, if they accept, they will be prompted to finish fabricating data before the on site interview. This timeframe will be several weeks instead of 45 minutes.

# Reviewer remark 8

This application does not clearly demonstrate an inductive methodology.

## Response

With the ROC analyses we apply an inductive methodology to assess the weight of the premise "the statistical test for data fabrication is significant" in support of the conclusion that the data were in fact fabricated. For project 2 and 3, we indeed do not demonstrate an inductive methodology because Project 2 applies abductive reasoning and project 3 uses statistical testing as an inductive methodology, which was validated in project 1 (and other work).

# Reviewer remark 9

The application does not provide a convincing basis for drawing sharp inferences regarding the types of fabrication that present the greatest risk given the modest number of available participants.

## Response

We are unsure of what the reviewer means with this comment, given that part of the proposal is to discover more about how data is fabricated. It is difficult to state which type of data fabrication poses the greatest risk if we do not know what types there are.

# Reviewer remark 10

In Project 3, the investigators plan to use existing software for publication screening before applying their proposed detection method. This screening step might be risky since this software may fail to identify certain types of data anomalies.

## Response

The reviewer correctly remarks that certain types of data anomalies might be missed. If missed, it does not get "cleared" so to speak: the flagging system only aims to identify potential problems, not to say that those that aren't flagged do not contain problems.

# Reviewer remark 11

It is not clear in the application why material flagged by ContentMine would necessarily be thought of as presenting fabrication risk, which suggests a substantial proportion of false positives.

## Response

No material will be flagged in relation to the subproject with ContentMine, we will only develop software and validate its performance in extracting information (not analyzing or qualifying those data).

# Reviewer remark 12

There are no details on the specific resources available to study staff in completion of the proposed research, such as computer capability, storage, security, and software programs. Similarly, there should be separate information about Content Mine, as they are a central resource for the development of proposed Phase 3 tools.

## Response

Tilburg University provides the research team with sufficient office space, computer facilities and support. Software programs used will all be free and open-source, and ContentMine has already provided the PI computing power on their servers. All sensitive files will be encrypted and stored on the PI's local copy with several encrypted backups.

### 2016-09-22 archive/response_ori_rev.md

We thank the reviewer for the time taken to look at and think about our proposal. Below, we respond point-by-point to the different weaknesses mentioned by the reviewer.

# Reviewer remark 1
The application does not provide clear evidence that the type of misconduct to which scientists admit is aligned with the kind of misconduct that the proposed methods would be able to address.

## Response

We never aimed to support such a claim; we only aimed to sketch the problem with the way estimates of data fabrication are now constructed. We fully agree with the reviewer that there is no way of knowing whether the data fabrication admitted to is the same as the data fabrication these methods could detect.

@@

# Reviewer remark 2

The application did not explain why it only focuses on social and medical sciences.

## Response

We focus only on the social- and medical sciences given the widespread use of randomized experimental procedures in these fields and our familiarity with the misconduct cases in these fields. We could expand to other fields with sufficient resources, but given the constraints of the current grant scheme we focused on these fields.

### 2016-09-26 archive/response_ori_rev.md

We thank the reviewer for the time taken to look at and think about our proposal. Below, we respond point-by-point to the different weaknesses mentioned by the reviewer.

# Reviewer remark 1
The application does not provide clear evidence that the type of misconduct to which scientists admit is aligned with the kind of misconduct that the proposed methods would be able to address.

## Response

We never aimed to support such a claim; we only aimed to sketch the problem with the way estimates of data fabrication are now constructed. We fully agree with the reviewer that there is no way of knowing whether the data fabrication admitted to is the same as the data fabrication these methods could detect. Project 1 and 2 were also designed to shed more light on the question how misconduct occurs so that they will help not only in identifying whether the proposed method are sufficient but also provide helpful data for developing new methods if the proposed ones fail.

@@

# Reviewer remark 2

The application did not explain why it only focuses on social and medical sciences.

## Response

We focus only on the social- and medical sciences given the widespread use of randomized experimental procedures in these fields and our familiarity with the misconduct cases in these fields. We could expand to other fields with sufficient resources, but given the constraints of the current grant scheme we focused on these fields. Regardless, the methods investigated can be applied to other fields as well.

### 2016-10-25 submission/manuscript.Rnw
Residual commit

<<prepwork, echo=FALSE,results=hide>>=
suppressPackageStartupMessages(if(!require(pROC)){install.packages('pROC')})
suppressPackageStartupMessages(library(pROC))
suppressPackageStartupMessages(if(!require(foreign)){install.packages('foreign')})
suppressPackageStartupMessages(library(foreign))
suppressPackageStartupMessages(if(!require(latex2exp)){install.packages('latex2exp')})
suppressPackageStartupMessages(library(latex2exp))
suppressPackageStartupMessages(if(!require(ggplot2)){install.packages('ggplot2')})
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(if(!require(gridExtra)){install.packages('gridExtra')})
suppressPackageStartupMessages(library(gridExtra))
suppressPackageStartupMessages(if(!require(xtable)){install.packages('xtable')})
suppressPackageStartupMessages(library(xtable))
suppressPackageStartupMessages(if(!require(httr)){install.packages('httr')})
suppressPackageStartupMessages(library(httr))

# Add ../ before running rmarkdown, or vice versa when not running there
x12 <- '../'
# x12 <- ''
@

@@

<<data prepper, echo=FALSE,results=hide>>=
# Dynamically generate path names
ml_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
qualtrics_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
dat_summary_file <- sprintf('%sdata/study_01/study1_res.csv', x12)
file <- sprintf('%sdata/study_01/raw_summary_results_fabrication_qualtrics.csv', x12)
res_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
ml_dat_file <- sprintf('%sdata/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav', x12)
summary_stat_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
pdf_file <- sprintf('%sarchive/gender_interaction.pdf', x12)

@@

# Compute the summary statistics for Many Labs
source(sprintf('%sfunctions/compute_summary_anch_ml.R', x12))
# Process the collected, fabricated data
source(sprintf('%sfunctions/process_qualtrics_anch_01.R', x12))
# Concatenate, analyze, and write out all ML and qualtrics data
# Uncomment this line to rerun, but take care: might take a while
if(!file.exists(sprintf('%sdata/study_01/study1_res.csv', x12)))
{
  set.seed(123);source(sprintf('%sfunctions/concatenate_analyze_01.R', x12))  
}
@

@@

The four anchoring studies for which results were collected were (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States. Each of the four studies provided summary results for a 2 (low/high anchoring) $\times$ 2 (male/female) factorial design. Throughout this study, the unit of analysis is a set of summary statistics (i.e., means, standard deviations, and test results) for the four anchoring studies from one respondent. For current purposes, a respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from. All materials, data, and analyses scripts are freely available on the OSF (\url{osf.io/b24pq}) and were preregistered (\url{osf.io/ejf5x}; deviations are explicated in this report).

@@

We downloaded thirty-six genuine datasets from the publicly available Many Labs (ML) project \citep[\url{osf.io/pqf9r};][]{klein2014}. The ML project replicated several effects across thirty-six locations, including the anchoring effect in the four studies mentioned previously. Considering the size of the ML project, the transparency of research results, and minimal individual gain for fraud, we assumed these data to be genuine. For each of the thirty-six locations, sample sizes, means, and standard deviations (four each) were computed for each of the four conditions in the four anchoring studies across the thirty-six locations (i.e., $3\times4\times4\times36$). We computed these summary statistics from the raw ML data, which were cleaned using the original analysis scripts from the ML project.

@@

A random sample of 1,000 researchers were approached via e-mail to participate in this study on April 25, 2016 (invitation: \url{osf.io/s4w8r}). The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-addresses saved). We informed the participating researchers that the study would require them to fabricate data and explicitly mentioned that we would investigate these data with statistical methods to detect data fabrication. We also clarified to the  respondents that they could stop at any time without providing a reason. If they wanted, respondents received a \$30 Amazon gift card as compensation for their participation if they were willing to enter their email address. They could win an additional \$50 Amazon gift card if they were one of three top fabricators. The provided email addresses were unlinked from individual responses upon sending the bonus gift cards. The full text of the Qualtrics survey is available at \url{osf.io/w984b}.

@@

We provided respondents with a template spreadsheet to fill out the fabricated data, in order to standardize the fabrication process without restraining the participant in how they chose to fabricate data. Figure \ref{fig1} depicts an example of this spreadsheet (original:  \url{osf.io/w6v4u}). We requested respondents to fill in the yellow cells with fabricated data, which includes means and the standard deviations for four conditions. Using these values, statistical tests are computed and shown in the "Current result" column instantaneously. If these results confirmed the hypotheses, a checkmark appeared as depicted in Figure \ref{fig1}. We required respondents to copy-paste the yellow cells into Qualtrics, to provide a standardized response format that could be automatically processed in the analyses.

@@

For each of these four tests to detect data fabrication ($SD_z$, Fisher test for the gender and interaction hypotheses, combined methods) we carried out sensitivity and specificity analyses using ROC-curves. ROC-curves indicate the sensitivity (i.e., True Positive Rate [TPR]) and specificity (i.e., True Negative Rate [TNR]) for various decision criteria (e.g., $\alpha=0, .01, .02, ..., .99, 1$). With these ROC-curves, informed decisions about optimal alpha levels can be made based on various criteria. In this case, we determine the optimal alpha level by finding that alpha level for which the combination of TPR and TNR were highest. For example, if $\alpha=.04$ results in $TPR=.30$ and $TNR=.70$, but $\alpha=.05$ results in $TPR=.5$ and $TNR=.5$, .05 was chosen as an optimal decision criterion based on the sample.

@@

The collected data included \Sexpr{table(dat_summary$type)[1]} genuine data from Many Labs 1 \citep[\url{osf.io/pqf9r};][]{klein2014} and \Sexpr{table(dat_summary$type)[2]} fabricated datasets(\url{osf.io/e6zys}). \Sexpr{sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))} participants did not participate for a bonus. Figure \ref{densities} shows a group-level comparison of the genuine- and fabricated $p$-values and effect sizes ($r$). Such group-level comparisons provide a general idea of the differences between the genuine- and fabricated data \citep[see also][]{Akhtar-Danesh2003}.

@@

@@

<<AUC for variance methods, echo=FALSE, results=tex>>=
selmaxmin <- grepl(Method, pattern = '^.maxmin_')
selsd <- grepl(x = Method, pattern = '^.SD_z')
row_table <- c("Homogeneous combined",
                    "Homogeneous study 1",
                    "Homogeneous study 2",
                    "Homogeneous study 3",
                    "Homogeneous study 4",
                    "Heterogeneous combined",
                    "Study 1 low condition",
                    "Study 1 high condition",
                    "Study 2 low condition",
                    "Study 2 high condition",
                    "Study 3 low condition",
                    "Study 3 high condition",
                    "Study 4 low condition",
                    "Study 4 high condition")
variances_table <- data.frame(Method = row_table, SDz = AUC[selsd], maxminz = AUC[selmaxmin])
names(variances_table) <- c("Method", "$SD_z$", "$maxmin_z$")
print(xtable(variances_table,
             caption = "Area Under the Curve (AUC) for the two statistical methods used to detect data fabrication based on variances. Homogeneous: assumes one population variance underlying all groups. Heterogeneous: assumes separate population variance per anchoring condition.",
             label = "auc_variances", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
@

<<generate variance ROC, echo=FALSE, results=hide>>=
if(!file.exists(sprintf('%sfigures/varianceplot.pdf', x12)))
{
  pdf(sprintf('%sfigures/varianceplot.pdf', x12), width = 8, height = 6)
  plot(fpr$variance_sd_p_overall_homo, tpr$variance_sd_p_overall_homo,
       type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance analysis',
       xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2, lty = 2)
  abline(a = 0, b = 1)
  lines(fpr$variance_sd_p_overall_hetero, tpr$variance_sd_p_overall_hetero,
        type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance heterogeneous',
        xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2, lty = 1)
  legend(x = 0, y = 1, bty = 'n', lty = c(2, 1), lwd = 2, legend = c('Homogeneous', 'Heterogeneous'))
  dev.off()
}
@

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/varianceplot.pdf}
\caption{PLACEHOLDER}
\label{varianceplot}
\end{center}
\end{figure}

@@

We asked researchers to fabricate data for nonsignificant effect sizes after inspecting whether the genuine data resembled a uniform distribution. Consequently, our hypothesis was that researchers who fabricate data would be unlikely to fabricate a uniform $p$-value distribution, given many researchers misinterpret the $p$-value (e.g., as the probability of an effect %REF
). However, as Table \ref{auc_fisher} indicates, the AUC for these methods are hardly better than chance. In other words, for effects that are specifically fabricated to be nonsignificant, researchers might not fabricate such large $p$-values to be suspicious.

<<AUC for single fisher methods, echo=FALSE, results=tex>>=
sel <- grepl(Method, pattern = '^(Fisher test)')
row_table <- Method[sel]
tabl <- data.frame(Method = row_table, AUC = AUC[sel])
print(xtable(tabl,
             caption = "Area Under the Curve (AUC) for PLACEHOLDER",
             label = "auc_fisher", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
@

@@

<<AUC for combined fisher methods, echo=FALSE, results=tex>>=
sel <- grepl(Method, pattern = 'Combined Fisher test')
row_table <- Method[sel]
tabl <- data.frame(Method = row_table, AUC = AUC[sel])
print(xtable(tabl,
             caption = "Area Under the Curve (AUC) for PLACEHOLDER",
             label = "auc_combined", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
@

@@

<<get massive statcheck data for checks, echo=FALSE, results=hide>>=
if(!file.exists(sprintf('%sdata/statcheck_dataset.csv', x12)))
{
  url <- 'https://github.com/chartgerink/2016statcheck_data/raw/master/statcheck_dataset.csv'
  # If link is broken, more persistent version availabl at
  # http://dx.doi.org/10.17026/dans-2cm-v9j9

@@

>>>>

<<prepwork, echo=FALSE,results=hide>>=
suppressPackageStartupMessages(if(!require(pROC)){install.packages('pROC')})
suppressPackageStartupMessages(library(pROC))
suppressPackageStartupMessages(if(!require(foreign)){install.packages('foreign')})
suppressPackageStartupMessages(library(foreign))
suppressPackageStartupMessages(if(!require(latex2exp)){install.packages('latex2exp')})
suppressPackageStartupMessages(library(latex2exp))
suppressPackageStartupMessages(if(!require(ggplot2)){install.packages('ggplot2')})
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(if(!require(gridExtra)){install.packages('gridExtra')})
suppressPackageStartupMessages(library(gridExtra))
suppressPackageStartupMessages(if(!require(xtable)){install.packages('xtable')})
suppressPackageStartupMessages(library(xtable))
suppressPackageStartupMessages(if(!require(httr)){install.packages('httr')})
suppressPackageStartupMessages(library(httr))
suppressPackageStartupMessages(if (!require(car)) install.packages('car'))
suppressPackageStartupMessages(library(car))
suppressPackageStartupMessages(if (!require(effects)) install.packages('effects'))
suppressPackageStartupMessages(library(effects))
suppressPackageStartupMessages(if (!require(lsr)) install.packages('lsr'))
suppressPackageStartupMessages(library(lsr))
suppressPackageStartupMessages(if (!require(data.table)) install.packages('data.table'))
suppressPackageStartupMessages(library(data.table))
suppressPackageStartupMessages(if (!require(dplyr)) install.packages('dplyr'))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(if (!require(reshape2)) install.packages('reshape2'))
suppressPackageStartupMessages(library(reshape2))

# Add ../ before running rmarkdown, or vice versa when not running there
x12 <- '../'
x12 <- ''
@

@@

<<data prepper, echo=FALSE,results=hide>>=
# Dynamically generate path names
ml_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
qualtrics_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
dat_summary_file <- sprintf('%sdata/study_01/study1_res.csv', x12)
file <- sprintf('%sdata/study_01/raw_summary_results_fabrication_qualtrics.csv', x12)
res_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
ml_dat_file <- sprintf('%sdata/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav', x12)
summary_stat_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
ml3_dat_file <- sprintf('%sdata/study_02/study_02-ml3_stroop/ML3 Stroop Data/ML3StroopRaw.csv', x12)
ml3_clean_file <- sprintf('%sdata/study_02/study_02-ml3_stroop/ML3 Stroop Data/StroopCleanSet.csv', x12)
pdf_file <- sprintf('%sarchive/gender_interaction.pdf', x12)

@@

# Study 1
# Compute the summary statistics for Many Labs
source(sprintf('%sfunctions/compute_summary_anch_ml.R', x12))
# Process the collected, fabricated data
source(sprintf('%sfunctions/process_qualtrics_anch_01.R', x12))
# Concatenate, analyze, and write out all ML and qualtrics data
# Uncomment this line to rerun, but take care: might take a while
if(!file.exists(sprintf('%sdata/study_01/study1_res.csv', x12)))
{
  set.seed(123);source(sprintf('%sfunctions/concatenate_analyze_01.R', x12))  
}

# Study 2
# Compute the processed raw data for Many Labs 3 stroop
source(sprintf('%sfunctions/compute_raw_stroop_ml3.R', x12))
@

@@

The four anchoring studies for which results were collected were (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States. Each of the four studies provided summary results for a 2 (low/high anchoring) $\times$ 2 (male/female) factorial design. Throughout this study, the unit of analysis is a set of summary statistics (i.e., means, standard deviations, and test results) for the four anchoring studies from one respondent. For current purposes, a respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from. All materials, data, and analyses scripts are freely available on the OSF (\url{https://osf.io/b24pq}) and were preregistered (\url{https:// .io/ejf5x}; deviations are explicated in this report).

@@

We downloaded thirty-six genuine datasets from the publicly available Many Labs (ML) project \citep[\url{https://osf.io/pqf9r};][]{klein2014}. The ML project replicated several effects across thirty-six locations, including the anchoring effect in the four studies mentioned previously. Considering the size of the ML project, the transparency of research results, and minimal individual gain for fraud, we assumed these data to be genuine. For each of the thirty-six locations, sample sizes, means, and standard deviations (four each) were computed for each of the four conditions in the four anchoring studies across the thirty-six locations (i.e., $3\times4\times4\times36$). We computed these summary statistics from the raw ML data, which were cleaned using the original analysis scripts from the ML project.

@@

A random sample of 1,000 researchers were approached via e-mail to participate in this study on April 25, 2016 (invitation: \url{https://osf.io/s4w8r}). The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-addresses saved). We informed the participating researchers that the study would require them to fabricate data and explicitly mentioned that we would investigate these data with statistical methods to detect data fabrication. We also clarified to the  respondents that they could stop at any time without providing a reason. If they wanted, respondents received a \$30 Amazon gift card as compensation for their participation if they were willing to enter their email address. They could win an additional \$50 Amazon gift card if they were one of three top fabricators. The provided email addresses were unlinked from individual responses upon sending the bonus gift cards. The full text of the Qualtrics survey is available at \url{https://osf.io/w984b}.

@@

We provided respondents with a template spreadsheet to fill out the fabricated data, in order to standardize the fabrication process without restraining the participant in how they chose to fabricate data. Figure \ref{fig1} depicts an example of this spreadsheet (original:  \url{https://osf.io/w6v4u}). We requested respondents to fill in the yellow cells with fabricated data, which includes means and the standard deviations for four conditions. Using these values, statistical tests are computed and shown in the "Current result" column instantaneously. If these results confirmed the hypotheses, a checkmark appeared as depicted in Figure \ref{fig1}. We required respondents to copy-paste the yellow cells into Qualtrics, to provide a standardized response format that could be automatically processed in the analyses.

@@

For each of these four tests to detect data fabrication ($SD_z$, Fisher test for the gender and interaction hypotheses, combined methods) we carried out sensitivity and specificity analyses using ROC-curves. ROC-analyses indicate the sensitivity (i.e., True Positive Rate [TPR]) and specificity (i.e., True Negative Rate [TNR]) for various decision criteria (e.g., $\alpha=0, .01, .02, ..., .99, 1$). With these ROC-curves, informed decisions about optimal alpha levels can be made based on various criteria. In this case, we determine the optimal alpha level by finding that alpha level for which the combination of TPR and TNR were highest. For example, if $\alpha=.04$ results in $TPR=.30$ and $TNR=.70$, but $\alpha=.05$ results in $TPR=.5$ and $TNR=.5$, .05 was chosen as an optimal decision criterion based on the sample. 
% Maybe include bootstrapped errors here.

@@

The collected data included \Sexpr{table(dat_summary$type)[1]} genuine data from Many Labs 1 \citep[\url{https://osf.io/pqf9r};][]{klein2014} and \Sexpr{table(dat_summary$type)[2]} fabricated datasets(\url{https://osf.io/e6zys}; \Sexpr{sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))} participants did not participate for a bonus).

Figure \ref{densities} shows a group-level comparison of the genuine- and fabricated $p$-values and effect sizes ($r$). Such group-level comparisons provide an overview of the differences between the genuine- and fabricated data \citep[see also][]{Akhtar-Danesh2003}. These distributions indicate little group differences between genuine- and fabricated data when nonsignificant effects are inspected (i.e., gender and interaction hypotheses) whereas there seem to be large group differences when we required subjects to fabricate significant data (i.e., condition hypothesis). From our own experience, and anecdotal evidence elsewhere \citep{BAILEY1991741}, large effects have previously raised initial suspicions. These data corroborate the idea that extremely large effect sizes (e.g., $r>.95$) might prove to be an easy-to-implement flag for potentially anomalous data (it is wise to seek for alternative explanations after flagging, however). Considering this, we also investigated how well effect sizes perform in detecting data fabrication (not preregistered). In the following sections, we investigate the performance of such statistical methods to detect data fabrication on an respondent-level basis.

@@

temp <- names(dat_summary)[grepl(names(dat_summary), pattern = "_p")]
df <- data.frame(Method = temp,
                     AUROC = NA,
                     CI.lb = NA,
                     CI.ub = NA)
Method <- c("$SD_z$ homogeneous all",
            "$SD_z$ study 1",
            "$SD_z$ study 2",
            "$SD_z$ study 3",
            "$SD_z$ study 4",
            "$maxmin_z$ homogeneous all",
            "$maxmin_z$ study 1",
            "$maxmin_z$ study 2",
            "$maxmin_z$ study 3",
            "$maxmin_z$ study 4",
            "$SD_z$ heterogeneous all",
            "$SD_z$ study 1 low condition",
            "$SD_z$ study 1 high condition",
            "$SD_z$ study 2 low condition",
            "$SD_z$ study 2 high condition",
            "$SD_z$ study 3 low condition",
            "$SD_z$ study 3 high condition",
            "$SD_z$ study 4 low condition",
            "$SD_z$ study 4 high condition",
            "$maxmin_z$ heterogeneous all",
            "$maxmin_z$ study 1 low condition",
            "$maxmin_z$ study 1 high condition",
            "$maxmin_z$ study 2 low condition",
            "$maxmin_z$ study 2 high condition",
            "$maxmin_z$ study 3 low condition",
            "$maxmin_z$ study 3 high condition",
            "$maxmin_z$ study 4 low condition",
            "$maxmin_z$ study 4 high condition",
            "Fisher test gender hypothesis",
            "Fisher test interaction hypothesis",
            "Combined Fisher test (3 results, $SD_z$ homogeneous)",
            "Combined Fisher test (3 results, $SD_z$ heterogeneous)",
            "Combined Fisher test (6 results, $SD_z$ homogeneous)",
            "Combined Fisher test (6 results, $SD_z$ heterogeneous)",
            "Effect sizes (1-r)")

@@

We applied two different operationalizations to inspect for data fabrication in the genuine- and fabricated datasets based on variance in the SDs. The $SD_z$ method \citep{simonsohn2013} inspects whether the variance of the SDs themselves varies sufficiently, and we tested another method that inspects the range of the SDs varies sufficiently. These two methods operate similarly, except for the final computation. Other operationalizations are possible and we invite others to reuse the data from this study (\url{https://osf.io/b24pq}).

Table \ref{auroc_variances} indicates that both methods show similar performance when inspected with the Area Under the Receiver Operating Curve (AUROC), but with a preference for $SD_z$. This preference is due to the variance of variances outperforming the range of variances when all studies are combined in one test and its past application \citep{simonsohn2013}. Throughout the rest of this section, we will only discuss the results of $SD_z$ further.

<<auroc for variance methods, echo=FALSE, results=tex>>=
selmaxmin <- grepl(Method, pattern = '^.maxmin_')
selsd <- grepl(x = Method, pattern = '^.SD_z')
row_table <- c("Homogeneous, all studies combined",
               "Homogeneous, study 1",
               "Homogeneous, study 2",
               "Homogeneous, study 3",
               "Homogeneous, study 4",
               "Heterogeneous, all studies combined",
               "Heterogeneous study 1, low anchor condition",
               "Heterogeneous study 1, high anchor condition",
               "Heterogeneous study 2, low anchor condition",
               "Heterogeneous study 2, high anchor condition",
               "Heterogeneous study 3, low anchor condition",
               "Heterogeneous study 3, high anchor condition",
               "Heterogeneous study 4, low anchor condition",
               "Heterogeneous study 4, high anchor condition")
variances_table <- data.frame(Method = row_table, SDz = AUC[selsd], maxminz = AUC[selmaxmin])
names(variances_table) <- c("Method", "AUROC $SD_z$", "AUROC $maxmin_z$")
print(xtable(variances_table,
             caption = "Area Under the Receiver Operating Curve (AUROC) for the two statistical methods used to detect data fabrication based on variances. Homogeneous: assumes one population variance underlying all groups. Heterogeneous: assumes separate population variance per anchoring condition.",
             label = "auroc_variances", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
@

The AUROC indicates the probability that a randomly drawn fabricated dataset is classified as fabricated before a randomly drawn genuine dataset is classified as fabricated \citep{doi:10.1148/radiology.143.1.7063747}. In other words, if AUROC $=.5$ this indicates that correctly classifying a randomly drawn dataset in this sample is equal to a coin flip. For this setting, we will regard any AUROC $<.6$ as plainly insufficient for detecting data fabrication, $.6\leq$ AUROC $<.7$ as failed, $.7\leq$ AUROC $<.8$ as sufficient, $.8\leq$ AUROC $<.9$ as good, and $.9\leq$ AUROC $\leq 1$ as excellent.

The AUROC for the variance of variance analyses is insufficient or sufficient depending on the assumption regarding population variances. Table \ref{auroc_variances} indicates that AUROC $=.423$ when homogeneous population variances are assumed, whereas AUROC $=.770$ when heterogeneous population variances are assumed. For the anchoring studies, homogeneous population variances across conditions seem unreasonable and greatly affect the performance of the statistical method. The method that incorporates heterogeneous population variances (i.e., one per anchoring condition) greatly improves the performance of the variance of variances analysis.

Further inspecting the heterogeneous variance of variances analysis indicates that no false positives occur until $\alpha=\Sexpr{seq(0, 1, .01)[max(which(tnr$variance_sd_p_overall_hetero == 1))]}$.

@@

We asked researchers to fabricate data for nonsignificant effect sizes after inspecting whether the genuine data resembled a uniform distribution. Consequently,  However, as Table \ref{auroc_fisher} indicates, the auroc for these methods are hardly better than chance. In other words, for effects that are specifically fabricated to be nonsignificant, researchers might not fabricate such large $p$-values to be suspicious.

<<auroc for single fisher methods, echo=FALSE, results=tex>>=
sel <- grepl(Method, pattern = '^(Fisher test)')
row_table <- Method[sel]
tabl <- data.frame(Method = row_table, AUROC = AUC[sel])
print(xtable(tabl,
             caption = "Area Under the Receiver Operating Curve (AUROC) for PLACEHOLDER",
             label = "auroc_fisher", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
@

@@

<<auroc for combined fisher methods, echo=FALSE, results=tex>>=
sel <- grepl(Method, pattern = 'Combined Fisher test')
row_table <- Method[sel]
tabl <- data.frame(Method = row_table, AUROC = AUC[sel])
print(xtable(tabl,
             caption = "Area Under the Receiver Operating Curve (AUROC) for PLACEHOLDER",
             label = "auroc_combined", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
@

@@

<<get massive statcheck data for checks, echo=FALSE, results=hide>>=
if(!file.exists(sprintf('%sdata/statcheck_dataset.csv', x12)))
{
  url <- 'https://github.com/chartgerink/2016statcheck_data/raw/master/statcheck_dataset.csv'
  # If link is broken, more persistent version available at
  # http://dx.doi.org/10.17026/dans-2cm-v9j9

@@

% Discuss alpha choice based on sample has large error (small sample).
% Only provides a first indication

% Comparison between methods not tested, large error given small sample.
% This provides just initial work

<<study 2 stuff, echo = FALSE, eval = FALSE>>=
# Computing the Stroop effect in ML3
mean(Stroop$StroopEffect,na.rm=TRUE)
t.test(Stroop$StroopEffect,y=NULL,alternative="two.sided",mu=0,paired=FALSE,var.equal=FALSE,conf.level=.95)
#Cohen's d for one sample
d<-mean(Stroop$StroopEffect,na.rm=TRUE)/sd(Stroop$StroopEffect,na.rm=TRUE)
d
@
